The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-24 paper/ms.tex
new plot and some text

For each photon in the simulation we have its initial position inside
the sphere, direction of propagation $\hat{k}_{in}$ and reduced
frequency $x_{in}$. The photon's propagation stops once they cross the
surface of the sphere. At this point we store the position, the outgoing direction
of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm obs}\cdot
\hat{k}_{\rm \hat{k}}$, that is the angle of the line of sight with
respect to the direction of the angular velocity. Following the notation
implemented in \cite{Zheng2013}. %we make the study of the anisotropic emission in
%terms of this angle.

@@

As a first approach we study the symmetry of the out-coming spectra
taking into account the line of view ($\theta$) of an observer. Figures 
\ref{fig:CentralSpec} and \ref{fig:HOMSpec} shows our findings, for 
both distributions the morphology of the line change as the line 
of sight of and observer changes. This is mainly due to the fact
that photons propagating at $\theta = pi/2.0$ feel an stronger 
angular momentum showing ... while photons in other direction feel
a less contribution.

@@

>>>>

For each photon in the simulation we have its initial position inside
the sphere, direction of propagation $\hat{k}_{in}$ and reduced
frequency $x_{in}$. The photon's propagation stops once they cross the
surface of the sphere. At this point we store the position, the outgoing direction
of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm obs}\cdot
\hat{k}$, that is the angle of the line of sight with
respect to the direction of the angular velocity. Following the notation
implemented in \cite{Zheng2013}. %we make the study of the anisotropic emission in
%terms of this angle.

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{f8.eps}
\end{center}
\caption{Geometry
    \label{fig:CentralSpec}}  
\end{figure}

@@

As a first approach we study the symmetry of the out-coming spectra
taking into account the line of view ($\theta$) of an observer. Figures 
\ref{fig:CentralSpec} and \ref{fig:HOMSpec} shows our findings, for 
both distributions the morphology of the line change as the line 
of sight of and observer changes. This is mainly due to the fact
that photons propagating at $\theta = \pi/2.0$ feels ... while photons in other direction feel
a less contribution.

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.40\textwidth]{nscattvsmu.eps}
\end{center}
\caption{Logarithm of the average number of scatterings as function of
  $\mu$. This is the general behavior for all models in particular this model
  is for $\tau=10^{5}$ and $V_{max}=300 km/s^{-1}$. \label{fig:Nscattvsmu}}    
\end{figure}
